Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
review existing lit

\section{Existing Literature} \label{existing_literature}
This section will introduce the topics of API design and software evolution and provide a brief review of studies that are directly related to our study.

\subsection{API Design} \label{api_design}
API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}. Examples of such decisions include whether or not to make use of the factory pattern or if an API should display errors only at compilation or only at runtime \cite{stylos2006comparing}. More trivial design problems, such as assigning names to API features or correctly naming user defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}. When facing such design decisions, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}. One of the most important qualities in an API is that the intent of the API is clear to the user, for example, using design patterns \cite{stylos2006comparing} \cite{shi2011empirical}. The design decisions reached during development of an API will effect the overall usability of the API, for better or worse. Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and the user of it \cite{clarke2004measuring}.

@@

\subsection{Related Work} \label{related_work}
The analysis of APIs in the context of software evolution has primarily focused on APIs that are a part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}. Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.

>>>>

\section{Existing Literature} \label{existing_literature}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.

\subsection{API Design} \label{api_design}
API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}. Examples of such decisions include whether or not to make use of the factory pattern or if an API should display errors only at compilation or only at runtime \cite{stylos2006comparing}. More trivial design problems, such as assigning names to API features or correctly naming user defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}. When facing such design decisions, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}. One of the most important qualities in an API is that the intent of the API is clear to the user, for example, ( "something is missing here") using design patterns \cite{stylos2006comparing} \cite{shi2011empirical}. The design decisions reached during development of an API will affect the overall usability of the API, for better or worse ( "too informal?"). Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.

@@

\subsection{Related Work} \label{related_work}
The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}. Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
